\section{Introduction}
Online social networks (OSNs) have seen a massive surge in usage over the past decade. The surge is also going hand in hand with the explosion of smart phone industry. More and more social interactions are now driven by media content like selfies and group selfies because of the ubiquitous nature of cameras. A sharp change in cultural aspects of online social interactions are evident and have also been studied in detail in papers like \cite{Souza2015}. Naturally, properties of real life interactions are now going to emerge in virtual social interactions. A study by Daniel Perez et.al \cite{7175072} observes that non-verbal communication has a strong effect on how a person is perceived at times of real world situations like interviews. These real world behaviours can also be extended to the virtual social world. With the rise of social media networks like Vine and Instagram, human to human non-verbal interactions have another dimension to manifest. 
The \cite{Souza2015} paper explores several of these properties of Instagram users, where they explore correlation of facial orientation, poses and smiles with parameters like country of origin of the selfie user, post frequency, likes received , number of faces in the pictures, gender and smile scores. Such studies give us interesting insights about the sharp rising phenomenon of selfies. However, there is another dimension that could be of potential use to understand the psychological and social reasons behind the posters. That dimension is sentiment. Sentiment is a emergent quantity, which can be quantified in terms of emotion, ontology and context. 