\section{Introduction}
The Art of story telling could be attributed to be one of the most ancient arts. It could be in the form of neolithic paintings to the egyptian hieroglyphs or among the elaborate epics of Illiad and oddyssey to the elaborate power plays of the Game of thrones, humans have always strived to record or create elaborate plots and stories. The human need of transferring experiences to others in different forms of creative arts, has ever so created the world as interesting as we see it. 
\par
The art of story telling has spawned and transformed several industries, including the very important entertainment industry. With progress of technology, entertainment industry has gone through several rejuvination cycles. Starting with plays to television, each technological advancement has created a new form of stories to be presented. The latest of these cycles was powered by the internet with the help of services like Youtube, Netflix, Hulu and Amazon. 

\par
Our work in this paper attempts to explore the validity of screenplay and screen writing theories in online social media. More specifically we try to measure perceptual sentiment across a video shared over an OSN, and look for strong evidence in frame sentiments to support generic screen writing theories. We eploy some of the most promising ideas of Visual and perceptual sentiment measurements \cite{SentiBank} and couple them with deep learning frameworks for increased generalized performance. Through this work we were able to detect strong clusters of trends of visually percieved sentiments that convey a strong overall story, independently from the actual audio track content. 
In the following sections the paper would try to elaborate on Screen play theories, the notion of Sentiments in media, then the paper would introduce you to the dataset we collected, then the techniques of examining the dataset. Finally we would conclude with our findings and discussions. \cite{7175072}

\footnote{www.vanityfair.com/hollywood/2016/02/king-bach-rocketjump-youtube-vine-stars}
\footnote{http://newmediarockstars.com/2015/04/youtubers-viners-attend-the-white-house-correspondents-dinner-gallery/}